Your Awesome Title

### 2021-11-02 Doc/respond_to_reviewer.Rmd

---
title: "Response to reviewers"
author: "Daijiang Li"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  pdf_document:
    highlight: zenburn
    keep_tex: no
    template: template/respond_to_reviewer.tex
    toc: yes
    toc_depth: 3
    latex_engine: xelatex
  html_document:
    css: template/respond_to_reviewer.css
    keep_md: no
    theme: readable
    toc: yes
  word_document: default
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
options(digits = 3, width = 88,
        # use pdf file automatically when compile to pdf
        knitr.graphics.auto_pdf = TRUE, 
        knitr.kable.NA = '')

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/respond_to_reviewer.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/respond_to_reviewer.css'
# change directory accordingly
if(!file.exists(tpl_1f <- 'template/respond_to_reviewer.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- 'template/respond_to_reviewer.css')) download.file(tpl_2, tpl_2f)

if(knitr::is_latex_output() | knitr::is_html_output()){
  library(kableExtra)
} else {
  options(kableExtra.auto_format = FALSE) # for docx
}
```

### 2021-11-02 Doc/ms.Rmd
update demo

---
title: "Your Awesome Title"
author: "Author One and Author Two"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: ../template/oikos.csl
bibliography: ../template/ref.bib
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align='center', cache=F, warning = FALSE, message = T, echo = FALSE)
options(digits = 3, width = 88)
```

@@

```{r tableName,results='asis',echo=FALSE, message=F, warning=F}
source("R/rcode.R")
knitr::kable(sprich, booktabs = T, caption = "Caption here.")
```

@@

```{r figName, fig.width=7, fig.asp=1, fig.cap="Your caption here."}
ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
  geom_point() + geom_smooth(method = "lm") +
  facet_wrap(~envi, scales = "free_x") + theme_bw()
```

Or if you already have the figure: 
And cite it as Figure \@ref(fig:fig2).

```{r fig2, out.width='70%', fig.cap="Caption here."}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```

@@

>>>>

---
title: "Your Awesome Title"
author: "Author One^1^* and Author Two^2^"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: template/doc_prefix.tex
      in_header: template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2:
    toc: no
    reference_docx: template/nature_style.docx
    number_sections: no
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/ecology.csl
bibliography: ref.bib
always_allow_html: yes
links-as-notes: true
notes-after-punctuation: false
---

```{r knitr_options, echo=FALSE}
library(knitr)
# rstudio will set the folder where .Rmd file seats as work directory
# set it back to the folder where .Rproj seats
opts_knit$set(root.dir = normalizePath("../")) 
opts_chunk$set(fig.align = 'center', cache = FALSE, warning = FALSE,
  message = TRUE, echo = FALSE, fig.pos = "H", out.extra = "")
options(digits = 3, width = 88,
        # use pdf file automatically when compile to pdf
        knitr.graphics.auto_pdf = TRUE, 
        knitr.kable.NA = '')

# download template files if not available
tpl_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/preamble.tex'
tpl_2 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/doc_prefix.tex'
tpl_3 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/Doc/template/nature_style.docx'
# bib_1 = 'https://raw.githubusercontent.com/daijiang/workflow_demo/master/template/ref.bib'
# change directory accordingly
if(!file.exists(tpl_1f <- 'template/preamble.tex')) download.file(tpl_1, tpl_1f)
if(!file.exists(tpl_2f <- 'template/doc_prefix.tex')) download.file(tpl_2, tpl_2f)
if(!file.exists(tpl_3f <- 'template/nature_style.docx')) download.file(tpl_3, tpl_3f)

if(knitr::is_latex_output() | knitr::is_html_output()){
  library(kableExtra)
} else {
  options(kableExtra.auto_format = FALSE) # for docx
}
```

\footnotesize

^1^Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA  
^2^Center for Computation & Technology, Louisiana State University, Baton Rouge, LA, USA

\* **Corresponding author**, email: daijianglee@gmail.com; 125 Life Science Building, Baton Rouge, LA 70803

\normalsize

@@

(ref:captionTable1) **Model coefficients of leaf senescence based on in situ data**. No space at the end of this line!!

```{r tableName,results='asis',echo=FALSE, message=F, warning=F}
source("R/rcode.R")
# linesep = c('', '', '', '', '', '\\addlinespace') 
# can be used within kable to specify linespace
knitr::kable(sprich, booktabs = T, caption = '(ref:captionTable1)')  %>%
 kableExtra::kable_styling(bootstrap_options = c("striped", "scale_down", "condensed", "hover"), 
                           latex_options = c("striped", "HOLD_position")) # , "scale_down"
```

@@

(ref:captionFig1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figName, fig.width=7, fig.asp=1, fig.cap="(ref:captionFig1)"}
ggplot(data = envi.sprich, aes(x = value, y = sprich)) +
  geom_point() + geom_smooth(method = "lm") +
  facet_wrap(~envi, scales = "free_x") + 
  theme_bw()
```

Or if you already have the figure:

And cite it as Figure \@ref(fig:fig2).

(ref:captionFig2) **No - or _ in the caption ref.** No space at the end of this line!

```{r fig2, out.width='70%', fig.cap="(ref:captionFig2)"}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```

@@

<div id="refs"></div>

\setcounter{page}{0}
\pagenumbering{arabic}
\setcounter{page}{1}

\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand {\thetable}{S\arabic{table}}
\renewcommand {\thefigure}{S\arabic{figure}}

# Supporting Information

## Figures

(ref:captionFigS1) **No - or _ in the caption ref.** No space at the end of this line!

```{r figS1, out.width='70%', fig.cap="(ref:captionFigS1)"}
knitr::include_graphics(path = paste0(normalizePath(getwd()), "/Figs/plot.pdf"))
```

### 2021-11-02 Doc/ms.tex
relocate template files
update demo

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Your Awesome Title},
            pdfauthor={Author One and Author Two},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

%%% Change title format to be more compact
\usepackage{titling}

% Create subtitle command for use in maketitle
\newcommand{\subtitle}[1]{
  \posttitle{
    \begin{center}\large#1\end{center}
    }
}

\setlength{\droptitle}{-2em}
  \title{Your Awesome Title}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{Author One and Author Two}
  \preauthor{\centering\large\emph}
  \postauthor{\par}
  \predate{\centering\large\emph}
  \postdate{\par}
  \date{2017-02-28 12:56:45}

\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

@@

\usepackage[utf8]{inputenc}

@@

\usepackage{setspace}
\doublespacing

@@

\usepackage{lineno}
\linenumbers

\renewcommand{\rmdefault}{cmr}

% flush left while keep identation
\makeatletter
\newcommand\iraggedright{%
  \let\\\@centercr\@rightskip\@flushglue \rightskip\@rightskip
  \leftskip\z@skip}
\makeatother

@@

% align only at left, not at right.
\iraggedright

@@

\section{Introduction}\label{introduction}

@@

\section{Methods}\label{methods}

@@

\subsection{Results}\label{results}

\paragraph{Tables}\label{tables}

@@

\begin{table}

\caption{\label{tab:tableName}Caption here.}
\centering
\begin{tabular}[t]{rr}
\toprule
Plot & sprich\\
\midrule
3294 & 31\\
3297 & 28\\
3299 & 26\\
3330 & 27\\
\bottomrule
\end{tabular}
\end{table}

@@

\paragraph{\texorpdfstring{Insert tables by \texttt{xtable} package in
R}{Insert tables by xtable package in R}}\label{insert-tables-by-xtable-package-in-r}

@@

\paragraph{Insert tables by hand}\label{insert-tables-by-hand}

@@

\paragraph{Figures}\label{figures}

@@

\begin{figure}

@@

\caption{Your caption here.}\label{fig:figName}
\end{figure}

Or if you already have the figure: And cite it as Figure \ref{fig:fig2}.

\begin{figure}

{\centering \includegraphics[width=0.7\linewidth]{/Users/dli/Github/workflow_demo/Figs/plot}

@@

\caption{Caption here.}\label{fig:fig2}
\end{figure}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-adair_single-pool_2010}{}
Adair, E. C. et al. 2010. Single-pool exponential decomposition models:
Potential pitfalls in their use in ecological studies. - Ecology 91:
1225--1236.

\hypertarget{ref-clark_loss_2008}{}
Clark, C. M. and Tilman, D. 2008. Loss of plant species after chronic
low-level nitrogen deposition to prairie grasslands. - Nature 451:
712--715.

\hypertarget{ref-eriksson_seed_1993}{}
Eriksson, O. and Ehrlén, J. 1993. Seed and microsite limitation of
recruitment in plant populations. - Oecologia 92: 361--366.

\hypertarget{ref-williamson_dissolved_1999}{}
Williamson, C. E. et al. 1999. Dissolved organic carbon and nutrients as
regulators of lake ecosystems: Resurrection of a more integrated
paradigm. - Limnology and Oceanography 44: 795--803.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  12pt,
]{article}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Your Awesome Title},
  pdfauthor={Author One1* and Author Two2},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% Make links footnotes instead of hotlinks:
\DeclareRobustCommand{\href}[2]{#2\footnote{\url{#1}}}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{geometry}
\geometry{verbose,letterpaper,margin=2.45cm}

@@

% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}
% \usepackage{textgreek}
\usepackage{babel}
% % \usepackage{microtype}
% % \usepackage{amsmath}
\usepackage[osf]{libertine}
\usepackage{libertinust1math}
\usepackage{inconsolata}

\usepackage{longtable}

@@

\usepackage{setspace}
% \doublespacing

@@

\usepackage{lineno}
% \linenumbers

\usepackage{flafter}
\usepackage{float}

% \renewcommand{\rmdefault}{cmr}

\usepackage[document]{ragged2e}

% % flush left while keep identation
% \makeatletter
% \newcommand\iraggedright{%
%   \let\\\@centercr\@rightskip\@flushglue \rightskip\@rightskip
%   \leftskip\z@skip}
% \makeatother
% \raggedright

% make pdf as default figure format
\DeclareGraphicsExtensions{.pdf,.png, %
    .jpg,.mps,.jpeg,.jbig2,.jb2,.JPG,.JPEG,.JBIG2,.JB2}

% \DeclareUnicodeCharacter{3B1}{\ensuremath{\alpha}}
% \DeclareUnicodeCharacter{3B2}{\ensuremath{\beta}}
% \DeclareUnicodeCharacter{0394}{$\Delta$}

\usepackage[labelsep=period]{caption}
\captionsetup{labelfont=bf}
% \usepackage{caption}
% \DeclareCaptionLabelSeparator{vline}{ \textbf{|} }
% \captionsetup{labelsep=vline, labelfont = {bf}}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Your Awesome Title}
\author{Author One\textsuperscript{1}* and Author Two\textsuperscript{2}}
\date{2021-11-02 15:56:55}

@@

% align only at left, not at right.
\renewcommand{\figurename}{{\textbf{Figure}}}
\renewcommand{\tablename}{{\textbf{Table}}}
% \iraggedright

\setstretch{1.5}
\footnotesize

\textsuperscript{1}Department of Biological Sciences, Louisiana State University, Baton Rouge, LA, USA\\
\textsuperscript{2}Center for Computation \& Technology, Louisiana State University, Baton Rouge, LA, USA

* \textbf{Corresponding author}, email: \href{mailto:daijianglee@gmail.com}{\nolinkurl{daijianglee@gmail.com}}; 125 Life Science Building, Baton Rouge, LA 70803

\normalsize

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{methods}{%
\section{Methods}\label{methods}}

@@

\hypertarget{results}{%
\subsection{Results}\label{results}}

\hypertarget{tables}{%
\paragraph{Tables}\label{tables}}

@@

\begin{table}[H]

\caption{\label{tab:tableName}\textbf{Model coefficients of leaf senescence based on in situ data}. No space at the end of this line!!}
\centering
\begin{tabular}[t]{rr}
\toprule
Plot & sprich\\
\midrule
\cellcolor{gray!6}{3294} & \cellcolor{gray!6}{31}\\
3297 & 28\\
\cellcolor{gray!6}{3299} & \cellcolor{gray!6}{26}\\
3330 & 27\\
\bottomrule
\end{tabular}
\end{table}

@@

\hypertarget{insert-tables-by-xtable-package-in-r}{%
\paragraph{\texorpdfstring{Insert tables by \texttt{xtable} package in R}{Insert tables by xtable package in R}}\label{insert-tables-by-xtable-package-in-r}}

@@

\hypertarget{insert-tables-by-hand}{%
\paragraph{Insert tables by hand}\label{insert-tables-by-hand}}

@@

\hypertarget{figures}{%
\paragraph{Figures}\label{figures}}

@@

\begin{verbatim}
## `geom_smooth()` using formula 'y ~ x'
\end{verbatim}

\begin{figure}[H]

@@

\caption{\textbf{No - or \_ in the caption ref.} No space at the end of this line!}\label{fig:figName}
\end{figure}

Or if you already have the figure:

And cite it as Figure \ref{fig:fig2}.

\begin{figure}[H]

{\centering \includegraphics[width=0.7\linewidth,]{/Users/dli/github/workflow_demo/Figs/plot}

@@

\caption{\textbf{No - or \_ in the caption ref.} No space at the end of this line!}\label{fig:fig2}
\end{figure}

More details can be found at \href{https://bookdown.org/yihui/bookdown/}{here}.

\hypertarget{references}{%
\section{References}\label{references}}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-adair_single-pool_2010}{}%
Adair, E. C., S. E. Hobbie, and R. K. Hobbie. 2010. Single-pool exponential decomposition models: Potential pitfalls in their use in ecological studies. Ecology 91:1225--1236.

\leavevmode\hypertarget{ref-clark_loss_2008}{}%
Clark, C. M., and D. Tilman. 2008. Loss of plant species after chronic low-level nitrogen deposition to prairie grasslands. Nature 451:712--715.

\leavevmode\hypertarget{ref-eriksson_seed_1993}{}%
Eriksson, O., and J. Ehrlén. 1993. Seed and microsite limitation of recruitment in plant populations. Oecologia 92:361--366.

\leavevmode\hypertarget{ref-williamson_dissolved_1999}{}%
Williamson, C. E., D. P. Morris, M. L. Pace, and O. G. Olson. 1999. Dissolved organic carbon and nutrients as regulators of lake ecosystems: Resurrection of a more integrated paradigm. Limnology and Oceanography 44:795--803.
\end{cslreferences}

@@

\setcounter{page}{0}
\pagenumbering{arabic}
\setcounter{page}{1}

\setcounter{figure}{0}
\setcounter{table}{0}
\renewcommand {\thetable}{S\arabic{table}}
\renewcommand {\thefigure}{S\arabic{figure}}

\hypertarget{supporting-information}{%
\section{Supporting Information}\label{supporting-information}}

\hypertarget{figures-1}{%
\subsection{Figures}\label{figures-1}}

\begin{figure}[H]

{\centering \includegraphics[width=0.7\linewidth,]{/Users/dli/github/workflow_demo/Figs/plot}

\caption{\textbf{No - or \_ in the caption ref.} No space at the end of this line!}\label{fig:figS1}
\end{figure}
